Fréchet Distance

### 2022-12-23 docs/paper.tex
add abstract

% \section*{Abstract}

\section{Introduction}
% motivation
At first, it seems that measuring the similarity between two curves
is a very theoretical problem, but it has many, not that obvious, practical applications.
It is used in Geo-Information-Systems (GIS) to 
quantify the similarity or quality of two maps \cite{lyu_partial-frechet-distance-based_2022},
find patterns in vehicle traffic or animal tracking data 
by trajectory analysis \cite{buchin_detecting_2011},
gesture recognition on touch devices like smartphones \cite{hu_research_2022},
and shape matching in the field of computer vision.

>>>>

\section*{Abstract}
% The Fréchet distance is a metric used to compare curves in a metric space
% that takes the course of the curves into account.
% This report will give an overview on the Fréchet distance 
% covering the general motivation, 
% the formal definition along with easy to understand explanations, 
% the weak and discrete variants, and algorithms to compute all of them.

The Fréchet distance is a metric used to compare curves in a metric space. 
It measures the similarity between two curves based on the overall shape and course of the curves. 
This report will provide an overview of the Fréchet distance, 
including its formal definition, weak and discrete variants, and algorithms for efficiently computing the distance. 
The report will also cover the general motivation for using the Fréchet distance 
and its applications in fields such as pattern recognition, computer vision, and geographic information systems. 
The report is structured to provide a comprehensive understanding of the Fréchet distance, 
including easy-to-understand explanations 
and a discussion of trade-offs between computational complexity and accuracy in the algorithms for computing the distance.

\section{Introduction}
% motivation
At first, it seems that measuring the similarity between two curves
is a very theoretical problem, but it has many, not that obvious, practical applications.
It is used in geographic information systems (GIS) to 
quantify the similarity or quality of two maps \cite{lyu_partial-frechet-distance-based_2022},
find patterns in vehicle traffic or animal tracking data 
by trajectory analysis \cite{buchin_detecting_2011},
gesture recognition on touch devices like smartphones \cite{hu_research_2022},
and shape matching in the field of computer vision.
